Robustness of MinD oscillation in \emph{Escherichia coli} with diverse cell shapes

### 2014-08-29 paper/paper.tex
fixed figure reference in paper Tested everything on quipu.

Figure~{arrow-pill-stadium} and Figure~{randst-plot-ave} show color
plots of time-averaged MinD overlayed by arrows depicting sequential
maxima that are global in space and local in time.  Our shapes that
are designed to look like Mannik cells show well the inadequacy of the
deterministic method of simulation and conversely the accuracy of the
stochastic method.  Our stochastic method movies (and arrow plots of
Figure~{randst-plot-ave}) show irregular location of maxima that is
similar to what is observed experimentally by Mannik. There is a
general bias towards back and forth behavoir, which can be seen in the
box plots of Figure~{box-mannik}, but the behavoir is irregular and
the location of the maxima vary a significant amount.  On the other
hand, the deterministic simulations show behavoir that is much too
regular when compared with experiment, exhibiting locations of maxima
that do not vary.  The deterministic method is seen to be inadequate.

@@

Judging that at this point that we have a fair idea of how our two
methods compare in terms of experimental acuracy, we are interested to
investigate the limits of the break down of regular activity, by
simulating large, regular, 'stadium' shapes.  These shapes have the
flattened, pancake like form of the assymetric cells, but from the top
down they look as pills do. In two dimensions they are composed of a
rectangle with two half ellipse connected on either end.  They are
also made to have a large volume that is similar to the Mannik shapes.

We find that both the stochastic and the deterministic solutions show
regular show back and forth behavoir in the stadium shaped cells, as
can be seen Figure~{box-stadium}.  This suggests that it is the
irregular shape of the Mannik cells,, not the size or their flattened
nature, that causes these cells be exhibit irregularity in MinD
oscillations.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD
    density. A density threshold is chosen and only maxima above this
    threshold are shown. The plots serve to illistrate what is
    observed in our movies. \fixme{how much of time of data is
      shown?}.  Although there is variation in the specific location
    of maxima on each edge of the cell, the behavoir for both of these
    regular shapes is robust and exhibits a back and forth oscillatory
    manner.  The wildtype pill shape behavoir matches well with
    experiment.  Regular pancake shapes have not been observed
    experimentally, but our stochastic simulations would suggest that
    they would exhibit regular robust oscillations similar to the pill
    shapes.  This is in contrast to the behavoir of Mannik cells seen
    in Figure~{randst-plot-ave}}
  \label{arrow-pill-stadium}
\end{figure}

Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
simulated with the stochastic method and with the deterministic
method, along with a plot taken from Mannik showing the location of
sequential MinD maxima in the experimental cells.  Like Mannik's, the
tips of the arrows in our plots show subsequent maxima, and the data
overlays a color plot of time averaged MinD concentration.  These
plots illustrate the adequacy of the stochastic method and inadequacy
of the deterministic one.  The stochastic plots show similar random behavoir to Manniks

>>>>

Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show color
plots of time-averaged MinD overlayed by arrows depicting sequential
maxima that are global in space and local in time.  Our shapes that
are designed to look like Mannik cells show well the inadequacy of the
deterministic method of simulation and conversely the accuracy of the
stochastic method.  Our stochastic method movies (and arrow plots of
Figure~\ref{randst-plot-ave}) show irregular location of maxima that is
similar to what is observed experimentally by Mannik. There is a
general bias towards back and forth behavoir, which can be seen in the
box plots of Figure~\ref{box-mannik}, but the behavoir is irregular and
the location of the maxima vary a significant amount.  On the other
hand, the deterministic simulations show behavoir that is much too
regular when compared with experiment, exhibiting locations of maxima
that do not vary.  The deterministic method is seen to be inadequate.

@@

Judging that at this point that we have a fair idea of how our two
methods compare with experiment, we investigate the limits of the
break down of regular activity, by simulating large, regular,
'stadium' shapes.  These shapes have the flattened, pancake like form
of the assymetric cells, but from the top down they look as pills
do. In two dimensions they are composed of a rectangle with two half
ellipse connected on either end.  They are also made to have a large
volume that is similar to the Mannik shapes.

We find that both the stochastic and the deterministic solutions show
regular back and forth oscillations the stadium shaped cells, as can
be seen Figure~\ref{box-stadium}.  This suggests that it is the irregular,
assymetric shape of the Mannik cells, not their size or their
flattened nature, that causes these cells to exhibit irregularity in
MinD oscillations.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
  \caption{Arrows depicting global maxima in space and local maxima in
    time overlayed on color plots of time averaged total MinD
    density. A density threshold is chosen and only maxima above this
    threshold are shown. The plots serve to illistrate what is
    observed in our movies. \fixme{how much of time of data is
      shown?}.  Although there is variation in the specific location
    of maxima on each edge of the cell, the behavoir for both of these
    regular shapes is robust and exhibits a back and forth oscillatory
    manner.  The wildtype pill shape behavoir matches well with
    experiment.  Regular pancake shapes have not been observed
    experimentally, but our stochastic simulations would suggest that
    they would exhibit regular robust oscillations similar to the pill
    shapes.  This is in contrast to the behavoir of Mannik cells seen
    in Figure~\ref{randst-plot-ave}}
  \label{arrow-pill-stadium}
\end{figure}

Figure~\ref{randst-plot-ave} shows a comparison of irregular shapes
simulated with the stochastic method and with the deterministic
method, along with a plot taken from Mannik showing the location of
sequential MinD maxima in the experimental cells.  Like Mannik's, the
tips of the arrows in our plots show subsequent maxima, and the data
overlays a color plot of time averaged MinD concentration.  These
plots illustrate the adequacy of the stochastic method and inadequacy
of the deterministic one.  The stochastic plots show similar random
behavoir to Manniks
